Using Blockchain to Create a Decentralised Security Model for Distributed Systems

### 2021-04-01 paper/paper.tex
Fixed spelling mistake

\chapter{Introduction}
\section{Univerity Cyberattacks}
In the summer of 2020 during the midst of the COVID-19 pandemic, universities and research institutions worldwide were working hard to understand the structure of the virus and develop a vaccine in an attempt to return to normality. However, whereas some countries were making fast progress in understanding the virus, others were falling behind, and the virus began to put a strain on healthcare, and increasing critique on governments. In order to keep up with the nations at the forefront of vaccine development, nations turned to state-sponsored cyberattacks in order to both hinder nations, and also obtain research and information about other countries' vaccine efforts. One such example was the threat group 'Cozy Bear', formally known as Advanced Persistent Threat (APT) 29. APT29 used a number of tools to target various organisations involved in COVID-19 vaccine development in Canada, the United States and the United Kingdom. The NCSC believe that the intention was highly likely stealing information and intellectual property relating to the vaccine \cite{APT29}.

>>>>

\chapter{Introduction}
\section{University Cyberattacks}
In the summer of 2020 during the midst of the COVID-19 pandemic, universities and research institutions worldwide were working hard to understand the structure of the virus and develop a vaccine in an attempt to return to normality. However, whereas some countries were making fast progress in understanding the virus, others were falling behind, and the virus began to put a strain on healthcare, and increasing critique on governments. In order to keep up with the nations at the forefront of vaccine development, nations turned to state-sponsored cyberattacks in order to both hinder nations, and also obtain research and information about other countries' vaccine efforts. One such example was the threat group 'Cozy Bear', formally known as Advanced Persistent Threat (APT) 29. APT29 used a number of tools to target various organisations involved in COVID-19 vaccine development in Canada, the United States and the United Kingdom. The NCSC believe that the intention was highly likely stealing information and intellectual property relating to the vaccine \cite{APT29}.
